Multiple quantum NMR in solids as a method of determination of Wigner--Yanase skew information

### 2021-05-10 manuscript.tex
Fix title and highlights

\title{Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information}

@@

%%Research highlights
\begin{highlights}
	\item multiple quantum NMR spectroscopy
	\item connection of the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
	\item the dependence of the number of entangled spins on temperature
\end{highlights}

>>>>

\title{Multiple quantum NMR in solids as a method of determination of Wigner--Yanase skew information}

@@

%%Research highlights
\begin{highlights}
	\item multiple quantum NMR spectroscopy
	\item connection between the Wigner-Yanase skew information and the second moment of the distribution of multiple quantum coherences
	\item the dependence of the number of entangled spins on temperature
\end{highlights}
